Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-01 W13report.tex
Renamed figures.  Fixed eqn 2/3 typo in a better way.

We model a source--free image (i.e.\ with a background described by a
Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.  
For an image with Gaussian noise convolved with a
Gaussian PSF with width $\sigma_g$ the density of peaks above a given
detection threshold, $\nu$ is given by 
\begin{equation}
n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}\sigma_g^{2}} \nu e^{-\nu^2 /2} 
\label{eq-theory}
\end{equation}
 To estimate the number of random
positive detections for a given image we must normalize this density
by the total number of realizations of the PSF within the image, i.e.,
\begin{equation}
N_{total}(>\nu) = n(\nu)*nrow*ncol/PSF_{FWHM}^2
\end{equation}
where nrow and ncol are the number of rows and columns in an images
and $PSF_{FWHM}$ is the FWHM of the PSF.  In difference image analysis, we expect
twice this number, since we are sensitive to both positive and negative--going
fluctuations.

@@

\begin{figure}
  \centering 
  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.60.eps}}
  \caption[]{ We plot here the expected change in the number of false positives
    as a function of detection threshold and noise misestimate.  The
    panels on these 3 pages are for three values of seeing.  In each panel the
    top pane shows what happens when the noise is under-estimated and
    the bottom shows what happens to the false positive rate when the
    noise is over-estimated.  In all cases the counts are for the
    total number of false positives in a single 4000x4072 pixel random
    Gaussian field.
    }
  \label{fig-fpthresh}
\end{figure}
\clearpage
\begin{figure}
  \ContinuedFloat 
  \centering 
  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.88.eps}}
  \caption[]{}
\end{figure} 
\clearpage
\begin{figure}
  \ContinuedFloat 
  \centering 
  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma1.20.eps}}
  \caption[]{}
\end{figure}

>>>>

We model a source--free image (i.e.\ with a background described by a
Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.  
For an image with Gaussian noise convolved with a
Gaussian PSF with width $\sigma_g$ the density of peaks above a given
detection threshold, $\nu$ is given by 
\begin{equation}
n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}} \nu e^{-\nu^2 /2} 
\label{eq-theory}
\end{equation}
To estimate the number of random
positive detections for a given image we must normalize this density
by the total number of realizations of the PSF within the image, i.e.,
\begin{equation}
N_{total}(>\nu) = n(>\nu)*nrow*ncol/ \sigma_g^2
\end{equation}
where nrow and ncol are the number of rows and columns.  
In difference image analysis, we expect
twice this number, since we are sensitive to both positive and negative--going
fluctuations.

@@

\begin{figure}
  \centering 
  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma060.eps}}
  \caption[]{ We plot here the expected change in the number of false positives
    as a function of detection threshold and noise misestimate.  The
    panels on these 3 pages are for three values of seeing.  In each panel the
    top pane shows what happens when the noise is under-estimated and
    the bottom shows what happens to the false positive rate when the
    noise is over-estimated.  In all cases the counts are for the
    total number of false positives in a single 4000x4072 pixel random
    Gaussian field.
    }
  \label{fig-fpthresh}
\end{figure}
\clearpage
\begin{figure}
  \ContinuedFloat 
  \centering 
  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma088.eps}}
  \caption[]{}
\end{figure} 
\clearpage
\begin{figure}
  \ContinuedFloat 
  \centering 
  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma120.eps}}
  \caption[]{}
\end{figure}
